---
title: "EDA GROUP PROJECT"
author: "TENG MAN"
date: "2023-01-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data = read.csv('eda_data.csv')
load = data$load
cr = data$cr
blend = data$blend
y = data$BSFC
data = data.frame(load,cr,blend,y)
data
```

To investigate the effect, the full interaction model is considered and written as follow:

$$
x_{ijkl} = \mu + \alpha_i + \beta_j + \gamma_k + {(\alpha\beta)}_{ij} + {(\beta\gamma)}_{jk} + {(\alpha\gamma)}_{ik} + {(\alpha\beta\gamma)}_{ijk} + \varepsilon_{ijkl}
$$

where

$l = 1$

$x_{ijkl}$ - BSFC values

$\mu$ - overall mean

$\alpha_i$ - the effect of the $i^{th}$ level of factor A (i.e.: load = {25,50,75,100}) for $i = 1,2,3,4$

$\beta_j$ - the effect of the $j^{th}$ level of factor B (i.e.: compress ratio = {16.5,17.0,17.5,18.0}) for $j = 1,2,3,4$

$\gamma_k$ - the effect of the $k^{th}$ level of factor C (i.e.: blend = {20,30,40,100}) for $k = 1,2,3,4$

${(\alpha\beta)}_{ij}$ - the interaction effect of the $i^{th}$ level of factor A and $j^{th}$ level of factor B

${(\beta\gamma)}_{jk}$ - the interaction effect of the $j\^{th}$ level of factor B and $k^{th}$ level of factor C

${(\alpha\gamma)}_{ik}$ - the interaction effect of the $i^{th}$ level of factor A and $k^{th}$ level of factor C

${(\alpha\beta\gamma)}_{ijk}$ - the interaction effect of the $i^{th}$ level of factor A, $j^{th}$ level of factor B and $k^{th}$ level of factor C

$\varepsilon_{ijkl}$ - random error

# Statistical Analysis

```{r}
res = lm(y ~ load*cr*blend, data)
summary(res)
```

```{r}
anova(res)
```

# Normal Plot

```{r}
effects <- abs(res$effects[-1])
qq <- qqnorm(effects) 
text(qq$x, qq$y, labels = names(effects))
```

# Main Effect Plot

```{r}
data
```

```{r}
library(gplots) # first download and install ‘gplots’ package, then activate it with a library command
plotmeans(y ~ load, data = data, xlab="load",ylab="BSFC", main="Main effect Plot",barcol="blue")
plotmeans(y ~ cr, data = data,xlab="compress ratio",ylab="BSFC", main="Main effect Plot",barcol="blue")
plotmeans(y ~ blend, data = data, xlab="blend",ylab="BSFC", main="Main effect Plot",barcol="blue")
```

# Interaction Effect Plot

```{r}
interaction.plot(x.factor = data$load, #x-axis variable
                 trace.factor = data$blend, #variable for lines
                 response = data$y, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "BSFC",
                 xlab = "Load",
                 col = c("pink", "blue", 'red',  'black'),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "blend")
```

```{r}
interaction.plot(x.factor = data$load, #x-axis variable
                 trace.factor = data$cr, #variable for lines
                 response = data$y, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "BSFC",
                 xlab = "Load",
                 col = c("pink", "blue", 'red',  'black'),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "blend")
```

```{r}
interaction.plot(x.factor = data$cr, #x-axis variable
                 trace.factor = data$blend, #variable for lines
                 response = data$y, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "BSFC",
                 xlab = "cr",
                 col = c("pink", "blue", 'red',  'black'),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "blend")
```

# APPENDIX - Model Adequacy Check

```{r}
plot(res)
```
